### 2021-05-26 LaTeX-ACM/sections/paper.tex
edits

Our proof-of-concept, \cm, is an extensible base class suitable for experiments. \cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third part, all operations are transparent, and we nearly eliminate the ability for adversarial network nodes to profit from front-running orders. In fact, we believe we are the first to design a decentralized application that actually leverages front-running (\ie miner extractable value~\cite{daian2019flash}) for the benefit of the system (see Section~\ref{sec:close}).

@@

A public blockchain is an open peer-to-peer network that maintains a set of transactions without a single entity in charge. In Ethereum, \emph{transactions} encode the bytecode of user-written \emph{decentralized applications} (DApps) to be stored on the blockchain; and the function calls made to the DApp. Every execution of every function call is validated by all honest, participating nodes to correct; a property that is robust against a fraction of faulty and malicious network nodes (or more precisely, their accumulated computational power). Once transactions are agreed upon, all honest participants will have identical sets of transactions in the same order. For Ethereum, this is conceptualized as the current state of a large \emph{virtual machine (EVM)} that is running many DApps.

@@

A miner can include as many transactions (typically preferring transactions that bid the highest for gas) that can fit under a pre-specified \textit{block gas limit}, which is algorithmically adjusted for every block. As of the time of writing, the limit is approximately 11M gas. Essentially, our main research question is how many on-chain trades can be executed without exceeding that limit. Later we also discuss several bytecode operations (\emph{opcodes}) that refund gas (\ie cost negative gas), which we heavily utilize in our optimizations.

@@

\paragraph[Centralized Exchanges (CEX)]{Centralized Exchanges (CEX)\eatpunct} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades. An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD). Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution. Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been leveled but are difficult to prove. Today, CEXes are often regulated as other money service businesses---this provides some ability for the government to conduct financial tracking but does little to provide consumer protection against fraud.

@@

\paragraph{Hybrid Designs.} Before on-chain dealers became prominent in the late 2010s, the most popular design was hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionality. Such decentralized exchanges (DEXes) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database. A landscape of DEX designs exist (\eg EtherDelta, 0x, IDEX, \etc): many avoid taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain (a regulatory hook). A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair, funds can still be indirectly stolen by a malicious exchange executing unauthorized trades, and server downtime is a common frustration for traders. An enhancement is to prove that trade execution is correct (\eg Loopring) but these proofs have blind spots (discussed in section~\ref{sec:rollups}).

>>>>

Our proof-of-concept, \cm, is an extensible base class suitable for experiments. \cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third party, all operations are transparent, and we nearly eliminate the ability for adversarial network nodes to profit from front-running orders. In fact, we believe we are the first to design a decentralized application that actually leverages front-running (\ie miner extractable value~\cite{daian2019flash}) for the benefit of the system (see Section~\ref{sec:close}).

@@

A public blockchain is an open peer-to-peer network that maintains a set of transactions without a single entity in charge. In Ethereum, \emph{transactions} encode the bytecode of user-written \emph{decentralized applications (DApps)} to be stored on the blockchain; and the function calls made to the DApp. Every execution of every function call is validated by all honest, participating nodes to correct; a property that is robust against a fraction of faulty and malicious network nodes (or more precisely, their accumulated computational power). Once transactions are agreed upon, all honest participants will have identical sets of transactions in the same order. For Ethereum, this is conceptualized as the current state of a large \emph{virtual machine (EVM)} that is running many DApps.

@@

A miner can include as many transactions (typically preferring transactions that bid the highest for gas) that can fit under a pre-specified \textit{block gas limit}, which is algorithmically adjusted for every block. As of the time of writing, the limit is approximately 11M gas. Essentially, our main research question is how many on-chain trades can be executed without exceeding that limit. Later, we also discuss several bytecode operations (\emph{opcodes}) that refund gas (\ie cost negative gas), which we heavily utilize in our optimizations.

@@

\paragraph[Centralized Exchanges (CEX)]{Centralized Exchanges (CEX)\eatpunct} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades. An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD). Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution. Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove. Today, CEXes are often regulated as other money service businesses---this provides some ability for the government to conduct financial tracking but does little to provide consumer protection against fraud.

@@

\paragraph{Hybrid Designs.} Before on-chain dealers became prominent in the late 2010s, the most popular design was hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionalities. Such decentralized exchanges (DEXes) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database. A landscape of DEX designs exist (\eg EtherDelta, 0x, IDEX, \etc): many avoid taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain (a regulatory hook). A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair, funds can still be indirectly stolen by a malicious exchange executing unauthorized trades, and server downtime is a common frustration for traders. An enhancement is to prove that trade execution is correct (\eg Loopring) but these proofs have blind spots (discussed in section~\ref{sec:rollups}).
